Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-06-19 analyses/scripts/orv_sys_rev_supplementary.Rmd
Shortened the old chunk for loading and cleaning data

#Rearrange the columns
compact_data_with_citation_keys <- compact_data_with_citation_keys %>% 
  relocate(c(title, bibtexkey), .before = publication_year) %>% 
  relocate(publication_year, .before = bibtexkey) %>% 
  relocate(c(x0_reviewer, category, author:language), 
           .after = collab_type
           )

compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
```
```{r echo=FALSE}
#' Count by collaboration types and make a bar plot
collab_types_count <- data_without_fmd %>%
    count(author_affiliation_type, sort = TRUE) %>% 
    mutate(author_affiliation_type = as_factor(author_affiliation_type))

>>>>

```{r}
#Paths to the datasets
args <- c(
  here::here("data", "review_data_long_cleaned.rds"),
  here::here("data", "compact_data_with_citation_keys_cleaned.rds")
  )
# Load the cleaned data 
long_data <- readRDS(args[1])

# The data with citations 
compact_data_with_citation_keys <- readRDS(args[2])

# Keep the human disease studies (NB: We only use the FMD papers for comparison)
long_data_no_fmd <- long_data %>% filter(disease != 'fmd')

data_without_fmd <- compact_data_with_citation_keys %>% 
  filter(disease != 'fmd')

# Filter the FMD data
fmd_data <- compact_data_with_citation_keys %>% 
  filter(disease == 'fmd') 
```

```{r echo=FALSE}
#' Count by collaboration types and make a bar plot
collab_types_count <- data_without_fmd %>%
    count(author_affiliation_type, sort = TRUE) %>% 
    mutate(author_affiliation_type = as_factor(author_affiliation_type))
